\sysfull

### 2018-04-15 paper/hwswsetup.tex
revision of text about manual code transform by alpaca

We evaluated \sys using six benchmarks summarized in Table~\ref{table:benchmark_table}, with their implementation is available via~\cite{coala_website}. Five benchmarks originate from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}: three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) were already implemented by Chain~\cite{chain} and Alpaca~\cite{alpaca}, while two (\textbf{dijkstra}, \textbf{fft}\footnote{Specifically, we re-implemented FFT based on the TI's accelerated FFT library~\cite{}.\todo{add reference}{Przemek}}) are added as new. The final one (\textbf{sort}) has been written from scratch. \todo{justify the selection of these benchmarks}{Przemek, Carlo, Amjad, Brandon}

@@

All applications were compiled using GCC version 3.8.0. \todo{Check if this still holds. provide optimization flag}{Przemek} We compare \sys against state-of-the-art task-based runtime Alpaca~\cite{alpaca}. For correct comparison, all benchmarks of \sys were divided into tasks in the same way as Alpaca. Moreover, since original Alpaca runtime was written in Clang, we transformed every benchmark manually into GCC-complaint code. \todo{Provide more information about porting to GCC from LLVM}{Brandon, Carlo}

We do not compare \sys against Chain~\cite{chain}, another task-based system, which is inferior to Alpaca in its performance. Also, we do not compare \sys to checkpointing-based systems, such as DINO~\cite{dino} or Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as both of them are build on top LLVM compiler, which performance is inferior to GCC compiler used in the evaluation of \sys \todo{Please check if the LLVM compiler argument makes sense}{Brandon}.

>>>>

We evaluated \sys using six benchmarks summarized in Table~\ref{table:benchmark_table}, with their implementation is available via~\cite{coala_website}. Five benchmarks originate from the MiBench testing suite~\cite{mibench,hicks_mibench2_2016}: three benchmarks (\textbf{ar}, \textbf{bc}, \textbf{cuckoo}) were already implemented by Chain~\cite{chain} and Alpaca~\cite{alpaca}, while two (\textbf{dijkstra}, \textbf{fft}\footnote{Specifically, we re-implemented FFT based on the TI's accelerated FFT library~\cite{}.\todo{add reference}{Przemek}}) are added as new. The final one (\textbf{sort}) has been written from scratch. \todo{justify the selection of these benchmarks}{Przemek, Carlo, Amjad, Brandon} All applications were compiled using GCC version 3.8.0. \todo{Check if this still holds. provide optimization flag}{Przemek}

@@

\textbf{Comparison with Alpaca and Alpaca Compiler Limitations.} We compare \sys against state-of-the-art task-based runtime Alpaca~\cite{alpaca}. For correct comparison, all benchmarks of \sys were divided into tasks in the same way as Alpaca. Since original Alpaca runtime was written in Clang, we had to transform every benchmark manually into GCC-complaint code. \todo{Provide more information about porting to GCC from LLVM}{Brandon, Carlo} This was a time-consuming process since a programmer needs to identify WAR dependencies \todo{check if we use WAR or write-after-read or anything else}{Przemek}, then change variables' names and modify instructions accordingly. Nota bene, our experiments based on the benchmarks we used here show that Alpaca compiled with GCC is about 30\%-40\% faster than Alpaca compiled with Clang. \todo{Provide concrete numbers for all applications}{Amjad} The speed improvement we got for Alpaca with GCC is however sacrificed by the above-mentioned error-prone manual code transformation process for which no compiler support exists thus far. \sys \emph{does not require any of such transformations}.

\textbf{Comparison of \sys against other Systems.} We do not compare \sys against Chain~\cite{chain}, another task-based system, which is inferior to Alpaca in its performance. Also, we do not compare \sys to checkpointing-based systems, such as DINO~\cite{dino} or Mementos~\cite{mementos} (cf. Section~\ref{sec:background_consistency}), as both of them are build on top LLVM compiler, which performance is inferior to GCC compiler used in the evaluation of \sys \todo{Please check if the LLVM compiler argument makes sense}{Brandon}.
